Adopting agile in the large: motivations, success factors and challenges

### 2014-04-16 journal/article.tex
Fixes to layout

In several cases there were more than one primary study presenting the
transformation of the same organization. Even if the transformation of a single
organization was described in many studies all sources that passed the inclusion
criterial were included. Studies presenting the same organization were treated
as one unit so that we could gain as much insight from each organization as
possible. There were also a few papers that presented multiple case studies, and
in those cases we treated each studied organization individually. As a result 42
unique organizations were identified in the primary studies. We use the word
\textit{case} to refer to the individual case organizations, and the word
\textit{study} to refer to the primary studies.

@@

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/organization_size.pdf}
    \caption{Distribution of organization sizes in primary studies}
    \label{fig:organization_size}
  \end{center}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/transformation_time.pdf}
    \caption{Publication years and reported start years of transformations}
    \label{fig:transformation_time}
  \end{center}
\end{figure}

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Method    &  Reported in studies   \\
        \midrule
        Scrum            &  25 \\
        XP               &  4  \\
        Scrum with XP    &  5  \\
        Scrum with Lean  &  6  \\
        Other            &  4  \\
        Not specified    &  1  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in the transformed organization}
    \label{table:agilemethods}
\end{table}

@@

@@

We investigated the initial state of the case organizations before the
transformation. The typical initial process model was described as waterfall, as
stated in 25 cases. In several cases the authors characterized the initial state
of the organization as ``\quote{traditional}''. CMMI was presented as a driver
for the original process in 4 cases. Other process models the studies named were
RUP [P19], Prince2 [P51], and Macroscope [P14]. In 9 cases the initial state was
not described.

The old model was described in most cases briefly and in a neutral sentiment.
Waterfall development in general was referred to as ``\quote{traditional,
plan-based methods}'' [P25], ``\quote{traditional phase-based approach}'' [P36],
or ``\quote{old fashioned process driven waterfall}'' [P23]. Korhonen [P25]
referred to the model presented by Royce \cite{Royce1970} when describing the
initial state.

In some cases specifics of the old model was criticized. The characteristics of
the old process models were described as having ``\quote{many gates and
sign-offs required by upper levels of management}'' [P9], ``\quote{lot of
bureaucracy in project management and a strict hierarchy of requirements
communication}'' [P39], and ``\quote{project managers typically used a
command-and-control philosophy}'' [P44].

In a few cases the initial process model was less rigid, and closer to the agile
model that was to be introduced. Examples of such loose process models were
described: ``\quote{The choice of development methodology is one of any number
of degrees of freedom granted to teams at Amazon. Development teams are expected
to solve their problems in the best way possible}'' [P3], ``\quote{the R&D group
leveraged a loose, waterfall-based process with an entrepreneurial culture}''
[P16]. Some organizations had even signs of agile development on team level
although the surrounding organization operated in a waterfall fashion. This was
described as ``\quote{Agile and Scrum were increasingly popular and emerging at
a grass-roots level, at a corporate level Yahoo! still embraced a more
traditional product development process}'' [P10], and ``\quote{some teams had
applied scrum on the team level, despite the surrounding organization that was
working with a waterfall software engineering model}'' [P26].

In a few cases the organization initailly lacked strict process. For instance
Long described the initial state in the following way: ``\quote{Project scope
was in constant flux. Well-meaning market and product owners routinely inserted
new requirements during product development.}'' [P30].

Some authors described the developement being originally organized in silos. For
instance Ranganath describes that ``\quote{Teams operated in silos.
Collaboration, shared purpose and ownership for outcomes were hard to find}''
[P40].

>>>>

In several cases there were more than one primary study presenting the
transformation of the same organization. Even if the transformation of a single
organization was described in many studies all sources that passed the inclusion
criterial were included. Studies presenting the same organization were treated
as one unit so that we could gain as much insight from each organization as
possible. There were also a few papers that presented multiple case studies, and
in those cases we treated each studied organization individually. As a result 42
unique organizations were identified in the primary studies. We use the word
\emph{case} to refer to the individual case organizations, and the word
\emph{study} to refer to the primary studies.

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/organization_size.pdf}
    \caption{Distribution of organization sizes in primary studies}
    \label{fig:organization_size}
  \end{center}
\end{figure}

@@

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/transformation_time.pdf}
    \caption{Publication years and reported start years of transformations}
    \label{fig:transformation_time}
  \end{center}
\end{figure}

\begin{table}[bh]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

@@

@@

\begin{table}[t]
    \begin{tabular}{ l r }
        \toprule
        Method    &  Reported in studies   \\
        \midrule
        Scrum            &  25 \\
        XP               &  4  \\
        Scrum with XP    &  5  \\
        Scrum with Lean  &  6  \\
        Other            &  4  \\
        Not specified    &  1  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in the transformed organization}
    \label{table:agilemethods}
\end{table}

@@

We investigated the initial state of the case organizations before the
transformation. The typical initial process model was described as waterfall, as
stated in 25 cases. In several cases the authors characterized the initial state
of the organization as ``traditional''. CMMI was presented as a driver for the
original process in 4 cases. Other process models the studies named were RUP
[P19], Prince2 [P51], and Macroscope [P14]. In 9 cases the initial state was not
described.

The old model was described in most cases briefly and in a neutral sentiment.
Waterfall development in general was referred to as ``traditional, plan-based
methods'' [P25], ``traditional phase-based approach'' [P36], or ``old fashioned
process driven waterfall'' [P23]. Korhonen [P25] referred to the model presented
by Royce \cite{Royce1970} when describing the initial state.

In some cases specifics of the old model was criticized. The characteristics of
the old process models were described as having ``many gates and sign-offs
required by upper levels of management'' [P9], ``lot of bureaucracy in project
management and a strict hierarchy of requirements communication'' [P39], and
``project managers typically used a command-and-control philosophy'' [P44].

In a few cases the initial process model was less rigid, and closer to the agile
model that was to be introduced. Examples of such loose process models were
described: ``The choice of development methodology is one of any number of
degrees of freedom granted to teams at Amazon. Development teams are expected to
solve their problems in the best way possible'' [P3], ``the R\&D group leveraged
a loose, waterfall-based process with an entrepreneurial culture'' [P16]. Some
organizations had even signs of agile development on team level although the
surrounding organization operated in a waterfall fashion. This was described as
``Agile and Scrum were increasingly popular and emerging at a grass-roots level,
at a corporate level Yahoo! still embraced a more traditional product
development process'' [P10], and ``some teams had applied scrum on the team
level, despite the surrounding organization that was working with a waterfall
software engineering model'' [P26].

In a few cases the organization initailly lacked strict process. For instance
Long describes the initial state in the following way: ``Project scope was in
constant flux. Well-meaning market and product owners routinely inserted new
requirements during product development.'' [P30].

Some authors describe the developement being originally organized in silos. For
instance Ranganath describes that ``Teams operated in silos. Collaboration,
shared purpose and ownership for outcomes were hard to find'' [P40].
